\hi{} and \ovi{} Emission from the Circum-Galactic Medium with a large sample of cosmological hydrodynamical simulations

### 2016-05-03 ms_oviemission.tex
add context about simulation in introduction

{\bf Why the CGM is important}

The hot and cold gas phases were indicated by \ovi{} and \hi{} ions in observation
commomly.

{\bf What can we gain from  \hi{} and \ovi{} in CGM}

\citet{Gutcke16} compared the column density profiles of \ovi{} and \hi{}
in CGM of galaxies of the cosmologycal hydrodynamical simulation suite 
NIHAO \citep{Wang15} with observations, studied the covering fraction of 
dense \hi{}, looked at the shape of the CGM and its chemical composition.
The simulations have a good agreement with observations and show observers
and modellers can compare with them in future studies.

However, the works mentioned above all relate to the absorption lines of
\hi{} and \ovi{}, there are rare simulations comparing the emission lines
of them with observations.
{\bf What is the advantage of emssion line of \hi{} and \ovi{}}

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

A complete galaxy formation model does not only require the understanding
of galactic components, such as stars and interstellar medium (ISM),
but also the gaseous medium surrounded galaxies and extended to virial
radius and beyond, the circumgalactic medium (CGM) namely.
The galactic components dominate the energy output of the system,
and always be focused by baryon counting \citep{Bell03}.
Compared to the cosmological baryonic fraction $\Omega_b/\Omega_m$,
stars and ISM come up significantly short on baryons. 
If we include the hot X-ray halo gas \citep{Baldry08,Yang09,
McGaugh10,Anderson10,Gupta12,Fang13}, the fracion is still under
the prediction from the cosmic baryonic fraction.

Galaxies have possibility apparently to exhibit a diffuse baryonic
content within CGM ({\bf citation}) which is observed via UV absorption
lines and has much lower temperature and density \citep{Werk13}.
Such CGM cannot be traced directly by X-ray emission or any other
radiative emission process.
The installation of the Cosmic Origins Spectrograph (COS) greatly
increased the capability of UV spectroscopy on the Hubble space
Telescope (HST) platform (e.g. Savage et al. 2010), enabling the
use of fainter quasar targets illuminating foreground galactic
haloes.
COS-Halos \citep{Tumlinson11, Thom12, Werk12, Werk13} has been 
working to investigate 
the properties of this elusive multiphase medium.
One of COS-Halos results demonstrated CGM is a large reservior
of baryons extanding far beyond the stellar disk of the galaxy.
This significant reservoir of halo gas clearly plays a central 
role in the cycling of baryons into and our of a galaxy, 
regulating this growth.

A number of large volume simulations \citep{Ford13, Ford15, Suresh15, Oppenheimer16} and 
zoom-in cosmological simulations \citep{Stinson12,Hummels13,Shull14} have 
investigated the properties of CGM and the link between 
galaxies and their metal-enriched CGM.
\citet{Ford15} do not include Active Galactic Nucleus (AGN) and do not
reproduce the \ovi{} bimodality, while \citet{Suresh15b} argue that
AGN feedback can remove the CGM around passive galaxies then reduce
the \ovi{} column densities around  passive galaxies.
\citet{Gutcke16} compared the column density profiles of \ovi{} and \hi{}
in CGM of galaxies of the cosmologycal hydrodynamical simulation suite 
NIHAO \citep{Wang15} with observations, studied the covering fraction of 
dense \hi{}, looked at the shape of the CGM and its chemical composition.
The simulations have a good agreement with observations and show observers
and modellers can compare with them in future studies.

Absorption line measurements have several limitations. 
Firstly, suitable background sources are rare so that there is 
typically only one or no background sight line per foreground
galaxy({\bf citation}). Because the area covered scales as the 
square of the impact parameter, the resulting measurements 
preferentially probe large impact parameters from foreground 
galaxies.
Finally, because of the 1D nature of absorption line constraints
it is often unclear what physical structure are probed.
Intergral field measurement of emission lines are complementary 
to absorption line measurements.
In particular, they allow us to directly obtain a 3D picture
of the distribution of gas in the CGM by combining the 2D map of
emission on the sky with line-of-sight velocity information.

@@

% Do Hot Haloes Around Galaxies Contain the Missing Baryons?
\bibitem[Anderson \& Bregman (2010)]{Anderson10} Anderson, M.~E., Bregman, J.~N.\ 2010, \apj, 714, 320

@@

% On the galaxy stellar mass function, the mass-metallicity relation and the implied baryonic mass function
\bibitem[Baldry et al.(2008)]{Baldry08} Baldry, I.~K., Glazebrook, K., Driver, S.~P.\ 2008, \mnras, 388, 945

@@

% On the Hot Gas Content of the Milky Way Halo
\bibitem[Fang et al.(2013)]{Fang13} Fang, T., Bullock, J., Boylan-Kolchin, M.\ 2013, \apj, 762, 20

%
\bibitem[Ford et al.(2013)]{Ford13} Ford, A.~B., Oppenheimer, B.~D., Dav{\`e}, R., et al.\ 2013, \mnras, 432, 89

%
\bibitem[Ford et al.(2015)]{Ford15} Ford, A.~B., Werk, J.~W., Dav{\`e}, R., et al.\ 2015, arXiv:1503.02084

@@

% A Huge Reservoir of Ionized Gas around the Milky Way: Accounting for the Missing Mass
\bibitem[Gupta et al. (2012)]{Gupta12} Gupta, A., Mathur, S., Krongold, Y., et al.\ 2012, \apj, 756L, 8

@@

%
\bibitem[Hummels et al.(2013)]{Hummels13} Hummels, C.~B., Bryan, G.~L., Smith, B.~D., et al.\ 2013, \mnras, 430,1548

@@

%
\bibitem[Oppenheimer et al,(2016)]{Oppenheimer16}
Oppenheimer, B.~D., Crain, R.~A., Schaye, J., et al.\ 2016, arXiv:1603.05984

@@

%
\bibitem[Shull (2014)]{Shull14}
Shull, J.~M.\ 2014, \apj, 784, 142

@@

%
\bibitem[Stinson et al.(2012)]{Stinson12} Stinson, G.~S., Brook, C., Prochaska, J.~X., et al.\ 2012, \mnras, 425,1270

@@

%
\bibitem[Suresh et al.(2015b)]{Suresh15b} Suresh, J., Rubin, K.~H.~R., Kannan, R., et al.\ 2015, arXiv:1511.00687

@@

% Galaxy Group in the SDSS DR4. III. The Luminosity and Stellar Mass Functions
\bibitem[Yang et al.(2009)]{Yang09} Yang, X., Mo, H.~J., van den Bosch, F.~C.\ 2009, \apj, 695, 900
